Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-27 report/report.tex
Conclusions summary

@@

We now have a firm idea of the technical feasibility of generating virtual cities from OpenStreetMap-data, including different types of road networks.
We have however yet to touch upon the importance for road network modelling in the broader context of 3D city reproduction.
Where exactly in the pipeline of reconstructing a virtual city does this happen, and what are the remaining challenges?
This will be the goal of this final scientific study: to place everything we have learnt so far in the broader context of GIS and city modeling, and the respective research fields.

>>>>

We now have a firm idea of the technical feasibility of generating virtual cities from OpenStreetMap-data, including different types of road networks.
We have however yet to touch upon the possibilities of road network modelling in the broader context of 3D city reproduction, and what are the remaining challenges for accurate 3D city reproduction?
What techniques can we use to complement our basic system of importing street and building data and create a rich and living virtual city?
In this section we will place everything we have learnt so far in the broader context of GIS and city modeling, focusing on the research fields of 3D media and city planning.

@@
